Reproducible Research in R: A Tutorial on How to Do the Same Thing More \highlighting{Than Once}

### 2021-12-03 manuscript.tex
reviewed but does not compile

%=================================================================
% Full title of the paper (Capitalized)
\Title{Reproducible Research in R: A Tutorial on How to Do the Same
Thing More \highlighting{Than Once}} %MDPI: the article type in the document is different with that in Susy, please confirm.

@@

% Authors, for the paper (add full first names)
\Author{\highlighting{Aaron Peikert~$^{1,2,*}$\href{https://orcid.org/0000-0001-7813-818X}{\orcidicon}} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.
, \highlighting{Caspar J. van Lissa~$^{3,4}$\href{https://orcid.org/0000-0002-0808-5024}{\orcidicon}} %MDPI: This author is different from susy. Please check.
 and Andreas M. Brandmaier~$^{1,5,6}$\href{https://orcid.org/0000-0001-8765-6982}{\orcidicon}}

@@

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, \hl{Berlin}, Germany\\%MDPI: Please add the post code.
$^{3}$ \quad \hl{Department} of Methodology \& Statistics---Utrecht \hl{University}, \hl{Faculty} of Social and Behavioral Sciences%MDPI: Please check the address order.  (order guide: Center / Laboratory / Group / Programme / Unit < Department / Division / Faculty / Campus / Institute / School < College / University / Universiti)
, \hl{Utrecht}, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, \hl{Utrecht}, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{\hl{Berlin, Germany, and London, UK}} %MDPI: 1. Please check if there are two separator affiliations. If so, please split them. 2. Please add the post code.
\\
$^{6}$ \quad MSB Medical School Berlin, \hl{Berlin}, Germany}

@@

% Keywords
\keyword{open science; computational reproducibility; preregistration;
R; R Markdown; make; GitHub; docker}%MDPI: 1. The upper case has been removed. Please confirm. 2. Please check if R is duplicated here.

@@

Scientists increasingly strive to make research data, materials, and
analysis code openly available. Sharing these digital research products
can increase scientific efficiency by enabling researchers to learn from
each other, reuse materials, and increase scientific reliability by
facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these
digital research products are reproducible. Reproducibility can be
defined as the ability of anyone to obtain identical results from the
\emph{same} data with the \hl{\emph{same}} %MDPI: Is the italic necessary? Can it be deleted?
 computer code (see~\citep{Peikert2019} \hl{for
details).} %MDPI: The structure of reference citation has been changed. So as the follows. Please confirm.
 The credibility of empirical research results
hinges on their objectivity. Objectivity in this context means, ``in
principle it {[}the research finding{]} can be tested and understood by
anybody.'' (\citep{popperLogicScientificDiscovery2002} p.~22). Only a
reproducible result meets these requirements. Therefore, reproducibility
has long been considered integral to empirical research. Unfortunately,
despite increasing commitment to open science practices and good will,
many projects can not yet be reproduced by other research teams
\citep{obels2020}. This is because there are various challenges to
making a research project reproducible (e.g., missing software
dependencies or ambiguous documentation of the exact computational steps
taken), and there is a lack of best practices for overcoming these
challenges (but see~\citep{vanlissa2020worcs}). With technological
advancement, however, it is now possible to make all digital products
related to a research project available in a manner that enables
automatic reproduction of the research project with minimal effort.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \highlighting{\emph{Multiple inconsistent versions of code, data, or both};} %MDPI: Is the italic necessary? Can it be deleted?
 for
  example, the data set may have changed over time because outliers were
  removed at a later stage or an item was later recoded; or, the
  analysis code may have been modified during the writing of a paper
  because a bug was removed at some point in time. It may then be
  unclear which version of code and data was used to produce some
  reported set of results.
\item
  \highlighting{\emph{Copy-and-paste errors};} for example, results are often manually
  copied from a statistical computing language into a text processor; if
  a given analysis is re-run and results are manually updated in the
  text processor, this may inadvertently lead to inconsistencies between
  the reported result and the reproduced result.
\item
  \highlighting{\emph{Undocumented or ambiguous order of computation};} for example,
  with multiple data and code files, it may be unclear which scripts
  should be executed in what order; or, some of the computational steps
  are documented (e.g., final analysis), but other steps were conducted
  manually without documentation (e.g., executing a command manually
  rather than in a script; copy-and-pasting results from one program to
  another).
\item
  \highlighting{\emph{Ambiguous software dependencies};} for example, a given analysis
  may depend on a specific version of a specific software package, or
  rely on software that might not be available on a different computer,
  or no longer exist at all; or a different version of the same software
  may produce different results.
\end{enumerate}

@@

\emph{Dependency tracking} helps automatically resolve dependencies
between project files. In essence, researchers provide a collection of
\emph{computational recipes}. A computational recipe describes how
inputs are processed to deterministically create a specific output in a
way that is automatically executable. The concept of computational
recipes is central to our understanding of reproducibility because it
enables a unified way to reproduce a project automatically. Similar to a
collection of cooking recipes, we can have multiple products
(\emph{targets}) with different ingredients (\emph{requirements}) and
different steps of preparation (\emph{recipes}). In the context of
scientific data analysis, targets are typically the final scientific
report (e.g., the one to be submitted to a journal) and produce possibly
intermediate %pls check (such as preprocessed data files, simulation
results, and analysis results). A workflow that involves renaming
variable names by hand in a graphical spreadsheet application, for
example, is therefore incompatible with automated reproducibility.
Another property of a computational recipe is that the same inputs
should always result in the same outputs. For most computer code (given
the same software is used), this property is fulfilled. However, one
noteworthy exception is the generation of pseudo-random numbers.
Whenever random numbers are used in a computation, it is only
reproducible if the random number generator generates the same numbers.
To ensure identical random numbers, users may fix the state of the
random number generated with a so-called seed (e.g.~\texttt{set.seed()}
in R), but they also need to guarantee that the pseudo-random number
generator is unchanged~(see~\citep{Peikert2019}).

@@

A second strategy is to save a so-called \texttt{Dockerfile}, which
contains only a textual description of all commands that need to be
executed to recreate the software environment. \texttt{Dockerfiles} are
tiny (the \hl{\texttt{Dockerfile}} %MDPI: Please add the accessed date.
 (\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile})
for this project has a size of only 1.55~KiB). However, they rely on the
assumption that all software repositories that provide the dependent
operating systems, pieces of software, and R packages will continue to
remain accessible and provide historic software versions. For proper
archiving, we therefore recommend storing a complete image of the
software environment, in addition to the \texttt{Dockerfile}. A more
comprehensive overview of the use of containerization in research
projects is given by Wiebels and Moreau~\citep{wiebelsLeveragingContainersReproducible2021}. Note that WORCS,
which we presented elsewhere~\citep{vanlissa2020worcs} relies on the R
package \texttt{renv}~\citep{R-renv} for software management. Although
\texttt{renv} is more lightweight and easier to use than \texttt{Docker}, it is not as comprehensive because it only
takes snapshots of the R packages instead of all software used.

To summarize, the workflow by Peikert and Brandmaier~\citep{Peikert2019} requires four
components (see \highlighting{Figure~\ref{figure1})} %MDPI: Figure 2.1 has been changed into Figure 1. Please confirm.
 dynamic document generation (using
\texttt{R\ Markdown}), version control (using \texttt{Git}), dependency
tracking (using \texttt{Make}), and software management (using
\texttt{Docker}). While \texttt{R\ Markdown} and \texttt{Git} are well
integrated into the R environment through RStudio, \texttt{Make} and
\texttt{Docker} require a level of expertise that is often beyond the
training of scholars outside the field of information technology. This
presents a considerable obstacle to the acceptance and implementation of
the workflow. To overcome this obstacle, we have developed the R package
\texttt{repro} that supports scholars in setting up, maintaining, and
reproducing research projects in R. Importantly, a reproducible research
project created with \texttt{repro} does not have the \texttt{repro}
package itself as a dependency. These projects will remain reproducible
irrespective of whether \texttt{repro} remains accessible in future.
Users do not need to have \texttt{repro} installed to reproduce a
project; in fact, they do not even need to have R installed because the
entire project can be rebuilt inside a container with R installed. In
the remainder, we will walk you through the creation of a reproducible
research project with the package~\texttt{repro}.

@@

The first step is to install the required software. We assume that you
have installed R (\citep{R-base} version 4.0.4) and RStudio
(\citep{rstudio} version 1.4) already but the tutorial will guide you in
detail through the installation of other necessary software with the
help of the R package {\texttt{repro}} 
(\url{https://github.com/aaronpeikert/repro})~\citep{R-repro}. In case you have either not installed R and RStudio or
are unsure if they are up-to-date, you might want to consult our
installation advice in the Online Supplementary Material
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) that covers the installation of all software
necessary for this tutorial in three steps. The
\hl{installation advice} %MDPI: Please add the accessed date.
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) may also help Windows users who have problems installing
\texttt{Docker}.

@@

For \texttt{Git} to recognize changes to a given file, you have to stage
and then commit these changes (this is the basic save action for a
project snapshot). One way to do this is through the visual user
interface in the RStudio \texttt{Git} pane (see \highlighting{Figure~\ref{figure2}).} %MDPI: Figure 3.1 has been changed into Figure 2. Please confirm.
 Click on
the empty box next to the file you want to stage. A checkmark then
indicates that the file is staged. After you have staged all of the
files you want, click on the commit button, explain in the commit
message why you made those changes, and then click on commit. This
stores a snapshot of the current state of the project.

@@

\textls[+15]{The idea of submitting code as part of a preregistration is not new (e.g.~\citep{wichertsDegreesFreedomPlanning2016}). A prominent preregistration platform, \hl{The Open Science Framework} %MDPI: Please add the accessed date.
(\url{https://osf.io/}), suggests submitting scripts alongside the preregistration of methods. In an informal literature search (we skimmed the first 300 results of Google Scholar with the keywords \texttt{\textls[+35]{("pre\ registration"\textbar{}"pre-registration"\textbar{}preregistration)\&(code\textbar{}script\textbar{}matlab\textbar{}}\linebreak python\textbar{}"R")}) we only found close to a dozen published articles that did include some form of script as part of their preregistration. Though the notion of preregistering code has been around for a while (cf.~\citep{steegenMeasuringCrowdAgain2014}), it has not gained much traction---perhaps because, to date, this has constituted an extra non-standard step in the research process. This tutorial integrates the preregistration of code into the reproducible research workflow by encouraging researchers to preregister the whole manuscript as a dynamic document.}

@@

We would like to note that PAC allows explicit comparison of the
preregistration and the final publication. Authors should
retrospectively summarize and justify any changes made to the
preregistered plan, e.g.~in the discussion of the \hl{final manuscript} %MDPI: Footnote is not allowed in this journal. The content has been moved here. Please confirm.
({In section {[}Preregistration as Code---a Tutorial{]} we
  conducted an actual PAC and summarize the changes we make to the
  preregistered code in the discussion}). During the analysis process,
authors can additionally maintain a running changelog to explain changes
in detail as they arise. Each entry in the changelog should explain the
reasoning behind the changes and link to the commit id that applied the
changes. This enables readers and reviewers to inspect individual
changes and make an informed judgment about their validity and
implications.

@@

Although researchers may use any form to preregister their planned
analyses (e.g., scripts), we suggest writing three functions for each
planned hypothesis: one to conduct the planned analysis, one to simulate
the expected data, and one to report the results. Using functions makes the
analysis more portable (i.e., it can easily be used for other datasets),
and facilitates repeated evaluation, as is the case in a simulation
study. The functions shown here do not contain executable code, but the
interested reader can find working functions in the \hl{online
supplementary materials}% MDPI: Please add the accessed date.
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation_funs.R}) that power the example below.

@@

\textls[-5]{This function should again accept the output of
\texttt{planned\_analysis()} as input. The output of this function
should be formatted in Markdown. The idea is to automatically generate
the full results section from the analysis. This way, the
preregistration not only specifies the computation but also how the its
results are reported. Various packages automatically generate
well-formatted Markdown outputs of statistical reports or even entire
tables of estimates or figures directly from R goal to help with this
objective. Packages like {\texttt{pander}}
(\url{https://github.com/Rapporter/pander})
\citep{pander}, {\texttt{stargazer}}
\mbox{(\url{https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf})}
\citep{stargazer}, {\texttt{apaTables}}
(\url{https://dstanley4.github.io/apaTables/articles/apaTables.html})
\citep{apaTables} and {\texttt{papaja}}
\mbox{(\url{http://frederikaust.com/papaja_man/})}
\citep{papaja} help you to create dynamically generated professional
looking results. The package {\texttt{report}}
(\url{https://github.com/easystats/report})~\citep{report} is particularly noteworthy because it not only generates
tables but also a straightforward interpretation of the effects as
actual prose (e.g., it verbally quantifies the size of an effect).}

@@

\begin{quote}
\hl{Navigate to} %MDPI: Please add the accessed date.
~\url{https://zenodo.org/login/} → Log in with GitHub
\end{quote}

@@

\begin{quote}
Log into zenodo.org → Account → \hl{GitHub} %MDPI: 1. Footnote is not allowed in this journal. The content has been moved here. Please confirm. 2. Please add the accessed date
~({\url{https://zenodo.org/account/settings/github/}})
\end{quote}

@@

Again, we propose a preregistration format that closely resembles a
classic journal article but uses simulated data and dynamic document
generation to create a document that starts out as a preregistration and
eventually becomes the final report. The complete preregistration source
is available in the \hl{online supplementary material}%MDPI: Please add the accessed date.
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd}). In this section, we show code excerpts of this
preregistration (formatted in monospace) and explain the rationale
behind them.

@@

We choose the following statistical procedure because many researchers
are familiar \hl{with it} %MDPI: Footnote is not allowed. The content has been moved here. Please confirm.
~(The \emph{t}-test and Mann-Whitney-Wilcoxon test
  are arguably the most often used hypothesis tests (according to
 ~\citep{fagerlandTtestsNonparametricTests2012, hortonStatisticalMethodsJournal2005}
  reports that 26\% of all studies employed a \emph{t}-test and 27\% employed a
  rank-based alternative in the \emph{New England Journal of Medicine}
  in 2005). The analytical strategy presented here is, in fact,
  suboptimal in several respects (the assumption of measurement
  invariance is untested
 ~\citep{putnickMeasurementInvarianceConventions2016}, the effect size
  is underestimated in the presence of measurement error
 ~\citep{frostCorrectingRegressionDilution2000}, the effect size is
  overestimated for highly skewed distributions
 ~\citep{stonehouseRobustnessTestsCombined1998}). The interested reader
  can use the \hl{provided code for the simulation}
~\mbox{(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R})} to verify that the \emph{t}-test provides unbiased
  effect sizes but the Mann-Whitney-Wilcoxon overestimates effect sizes
  with increasing sample size and skewness.):

@@

Together with the function \texttt{simulate\_data()} (not shown here),
the function \texttt{planned\_\linebreak analysis()} can be used to justify the
planned sample size. To that end, \texttt{simulate\_data()} is
repeatedly called with increased sample sizes and the proportion of
significant results (power) is recorded. The results for such a Monte
Carlo simulation for this example are visualized in \highlighting{Figure~\ref{figure3}.} %MDPI:  Figure 5.1 has been changed into Figure 3. Please confirm.
 The code
for this power analysis can be found in the \hl{online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R}). The next snippet shows how we integrated the
results dynamically into the preregistration (the origin of the
R-variables \texttt{minn}, \texttt{choosen\_power}, and
\texttt{choosen\_d} is not shown).

@@

Following the recommendations outlined in this paper, we did not access
the data when we initially wrote this code. We therefore did not know
the exact format the data would have. This means that we did need to
change our preregistration after accessing the data to include i.e.,~the
recoding of gender (lines 17--22) and the items\hl{ (lines 23--26).} %MDPI: Footnote is not allowed. The content has been moved here. Please confirm.
 ({We
  invite the reader to evaluate the changes we made to the preregistered
  code. Either on \hl{GitHub}
  (\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg...main})
  → ``Files changed'' or directly in Git with
  \texttt{git\ diff\ v0.0.1.1-prereg\ preregistration.Rmd}.}) This is our
summary of what we changed:

@@

\begin{verbatim}
The Welch Two Sample t-test testing the difference of machiavellianism by gender
(mean in group male = 0.96, mean in group female = 0.79) suggests that the
effect is - negative, statistically significant, and small (difference = -0.17,
95% CI [0.12, 0.22], t(887.46) = 6.38, p < 0.001; Cohen's d = 0.43, 95% CI [0.30,
0.56])
\end{verbatim}
\end{adjustwidth}
\begin{paracol}{2}
%\linenumbers
\switchcolumn

@@

Supplementary Materials{\hl{\quad \quad}}%The following are available online at www.mdpi.com/xxx/s1, Figure S1: title, Table S1: title, Video S1: title.

@@

\funding{\hl{\quad \quad}} %This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{\hl{\quad \quad}} %In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.

\informedconsent{\hl{\quad \quad}} %Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans. Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Reproducible Research in R: A Tutorial on How to Do the Same
Thing More \highlighting{Than Once}}

@@

% Authors, for the paper (add full first names)
\Author{\highlighting{Aaron Peikert~$^{1,2,*}$\href{https://orcid.org/0000-0001-7813-818X}{\orcidicon}}
, \highlighting{Caspar J. van Lissa~$^{3,4}$\href{https://orcid.org/0000-0002-0808-5024}{\orcidicon}}
 and Andreas M. Brandmaier~$^{1,5,6}$\href{https://orcid.org/0000-0001-8765-6982}{\orcidicon}}

@@

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, Unter den Linden 6, \mbox{10117 Berlin, Germany}
$^{3}$ \quad \hl{Department} of Methodology \& Statistics---Utrecht \hl{University}, \hl{Faculty} of Social and Behavioral Sciences
, \hl{Utrecht}, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, \hl{Utrecht}, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{\hl{Berlin, Germany, and London, UK}}\\
$^{6}$ \quad MSB Medical School Berlin, \hl{Berlin}, Germany}

@@

% Keywords
\keyword{open science; computational reproducibility; preregistration;
R; R Markdown; Make; GitHub; Docker}

@@

Scientists increasingly strive to make research data, materials, and
analysis code openly available. Sharing these digital research products
can increase scientific efficiency by enabling researchers to learn from
each other, reuse materials, and increase scientific reliability by
facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these
digital research products are reproducible. Reproducibility can be
defined as the ability of anyone to obtain identical results from the
\emph{same} data with the \hl{\emph{same}}
 computer code (see~\citep{Peikert2019} \hl{for
details).}
 The credibility of empirical research results
hinges on their objectivity. Objectivity in this context means, ``in
principle it {[}the research finding{]} can be tested and understood by
anybody.'' (\citep{popperLogicScientificDiscovery2002} p.~22). Only a
reproducible result meets these requirements. Therefore, reproducibility
has long been considered integral to empirical research. Unfortunately,
despite increasing commitment to open science practices and good will,
many projects can not yet be reproduced by other research teams
\citep{obels2020}. This is because there are various challenges to
making a research project reproducible (e.g., missing software
dependencies or ambiguous documentation of the exact computational steps
taken), and there is a lack of best practices for overcoming these
challenges (but see~\citep{vanlissa2020worcs}). With technological
advancement, however, it is now possible to make all digital products
related to a research project available in a manner that enables
automatic reproduction of the research project with minimal effort.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \highlighting{\emph{Multiple inconsistent versions of code, data, or both};}
 for
  example, the data set may have changed over time because outliers were
  removed at a later stage or an item was later recoded; or, the
  analysis code may have been modified during the writing of a paper
  because a bug was removed at some point in time. It may then be
  unclear which version of code and data was used to produce some
  reported set of results.
\item
  \highlighting{\emph{Copy-and-paste errors};} for example, results are often manually
  copied from a statistical computing language into a text processor; if
  a given analysis is re-run and results are manually updated in the
  text processor, this may inadvertently lead to inconsistencies between
  the reported result and the reproduced result.
\item
  \highlighting{\emph{Undocumented or ambiguous order of computation};} for example,
  with multiple data and code files, it may be unclear which scripts
  should be executed in what order; or, some of the computational steps
  are documented (e.g., final analysis), but other steps were conducted
  manually without documentation (e.g., executing a command manually
  rather than in a script; copy-and-pasting results from one program to
  another).
\item
  \highlighting{\emph{Ambiguous software dependencies};} for example, a given analysis
  may depend on a specific version of a specific software package, or
  rely on software that might not be available on a different computer,
  or no longer exist at all; or a different version of the same software
  may produce different results.
\end{enumerate}

@@

\emph{Dependency tracking} helps automatically resolve dependencies
between project files. In essence, researchers provide a collection of
\emph{computational recipes}. A computational recipe describes how
inputs are processed to deterministically create a specific output in a
way that is automatically executable. The concept of computational
recipes is central to our understanding of reproducibility because it
enables a unified way to reproduce a project automatically. Similar to a
collection of cooking recipes, we can have multiple products
(\emph{targets}) with different ingredients (\emph{requirements}) and
different steps of preparation (\emph{recipes}). In the context of
scientific data analysis, targets are typically the final scientific
report (e.g., the one to be submitted to a journal) and possibly
intermediate results (such as preprocessed data files, simulation
results, and analysis results). A workflow that involves renaming
variable names by hand in a graphical spreadsheet application, for
example, is therefore incompatible with automated reproducibility.
Another property of a computational recipe is that the same inputs
should always result in the same outputs. For most computer code (given
the same software is used), this property is fulfilled. However, one
noteworthy exception is the generation of pseudo-random numbers.
Whenever random numbers are used in a computation, it is only
reproducible if the random number generator generates the same numbers.
To ensure identical random numbers, users may fix the state of the
random number generated with a so-called seed (e.g.~\texttt{set.seed()}
in R), but they also need to guarantee that the pseudo-random number
generator is unchanged~(see~\citep{Peikert2019}).

@@

A second strategy is to save a so-called \texttt{Dockerfile}, which
contains only a textual description of all commands that need to be
executed to recreate the software environment. \texttt{Dockerfiles} are
tiny (the \hl{\texttt{Dockerfile}}
 (\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile})
for this project has a size of only 1.55~KiB). However, they rely on the
assumption that all software repositories that provide the dependent
operating systems, pieces of software, and R packages will continue to
remain accessible and provide historic software versions. For proper
archiving, we therefore recommend storing a complete image of the
software environment, in addition to the \texttt{Dockerfile}. A more
comprehensive overview of the use of containerization in research
projects is given by Wiebels and Moreau~\citep{wiebelsLeveragingContainersReproducible2021}. Note that WORCS,
which we presented elsewhere~\citep{vanlissa2020worcs} relies on the R
package \texttt{renv}~\citep{R-renv} for software management. Although
\texttt{renv} is more lightweight and easier to use than \texttt{Docker}, it is not as comprehensive because it only
takes snapshots of the R packages instead of all software used.

To summarize, the workflow by Peikert and Brandmaier~\citep{Peikert2019} requires four
components (see \highlighting{Figure~\ref{figure1})}
 dynamic document generation (using
\texttt{R\ Markdown}), version control (using \texttt{Git}), dependency
tracking (using \texttt{Make}), and software management (using
\texttt{Docker}). While \texttt{R\ Markdown} and \texttt{Git} are well
integrated into the R environment through RStudio, \texttt{Make} and
\texttt{Docker} require a level of expertise that is often beyond the
training of scholars outside the field of information technology. This
presents a considerable obstacle to the acceptance and implementation of
the workflow. To overcome this obstacle, we have developed the R package
\texttt{repro} that supports scholars in setting up, maintaining, and
reproducing research projects in R. Importantly, a reproducible research
project created with \texttt{repro} does not have the \texttt{repro}
package itself as a dependency. These projects will remain reproducible
irrespective of whether \texttt{repro} remains accessible in future.
Users do not need to have \texttt{repro} installed to reproduce a
project; in fact, they do not even need to have R installed because the
entire project can be rebuilt inside a container with R installed. In
the remainder, we will walk you through the creation of a reproducible
research project with the package~\texttt{repro}.

@@

The first step is to install the required software. We assume that you
have installed R (\citep{R-base} version 4.0.4) and RStudio
(\citep{rstudio} version 1.4) already but the tutorial will guide you in
detail through the installation of other necessary software with the
help of the R package {\texttt{repro}} 
(\url{https://github.com/aaronpeikert/repro})~\citep{R-repro}. In case you have either not installed R and RStudio or
are unsure if they are up-to-date, you might want to consult our
installation advice in the Online Supplementary Material
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) that covers the installation of all software
necessary for this tutorial in three steps. The
\hl{installation advice}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) may also help Windows users who have problems installing
\texttt{Docker}.

@@

For \texttt{Git} to recognize changes to a given file, you have to stage
and then commit these changes (this is the basic save action for a
project snapshot). One way to do this is through the visual user
interface in the RStudio \texttt{Git} pane (see \highlighting{Figure~\ref{figure2}).}
 Click on
the empty box next to the file you want to stage. A checkmark then
indicates that the file is staged. After you have staged all of the
files you want, click on the commit button, explain in the commit
message why you made those changes, and then click on commit. This
stores a snapshot of the current state of the project.

@@

\textls[+15]{The idea of submitting code as part of a preregistration is not new (e.g.~\citep{wichertsDegreesFreedomPlanning2016}). A prominent preregistration platform, \href{https://osf.io/}{The Open Science
Framework}, suggests submitting scripts alongside the preregistration of methods. In an informal literature search (we skimmed the first 300 results of Google Scholar with the keywords \texttt{\textls[+35]{("pre\ registration"\textbar{}"pre-registration"\textbar{}preregistration)\&(code\textbar{}script\textbar{}matlab\textbar{}}\linebreak python\textbar{}"R")}) we only found close to a dozen published articles that did include some form of script as part of their preregistration. Though the notion of preregistering code has been around for a while (cf.~\citep{steegenMeasuringCrowdAgain2014}), it has not gained much traction---perhaps because, to date, this has constituted an extra non-standard step in the research process. This tutorial integrates the preregistration of code into the reproducible research workflow by encouraging researchers to preregister the whole manuscript as a dynamic document.}

@@

We would like to note that PAC allows explicit comparison of the
preregistration and the final publication. Authors should
retrospectively summarize and justify any changes made to the
preregistered plan, e.g.~in the discussion of the \hl{final manuscript}
({In section {[}Preregistration as Code---a Tutorial{]} we
  conducted an actual PAC and summarize the changes we make to the
  preregistered code in the discussion}). During the analysis process,
authors can additionally maintain a running changelog to explain changes
in detail as they arise. Each entry in the changelog should explain the
reasoning behind the changes and link to the commit id that applied the
changes. This enables readers and reviewers to inspect individual
changes and make an informed judgment about their validity and
implications.

@@

Although researchers may use any form to preregister their planned
analyses (e.g., scripts), we suggest writing three functions for each
planned hypothesis: one to conduct the planned analysis, one to simulate
the expected data, and one to report the results. Using functions makes the
analysis more portable (i.e., it can easily be used for other datasets),
and facilitates repeated evaluation, as is the case in a simulation
study. The functions shown here do not contain executable code, but the
interested reader can find working functions in the \hl{online
supplementary materials}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation_funs.R}) that power the example below.

@@

\textls[-5]{This function should again accept the output of
\texttt{planned\_analysis()} as input. The output of this function
should be formatted in Markdown. The idea is to automatically generate
the full results section from the analysis. This way, the
preregistration not only specifies the computation but also how the its
results are reported. Various packages automatically generate
well-formatted Markdown outputs of statistical reports or even entire
tables of estimates or figures directly from R goal to help with this
objective. Packages like
\href{https://github.com/Rapporter/pander}{\texttt{pander}}
\citep{pander},
\href{https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf}{\texttt{stargazer}}
\citep{stargazer},
\href{https://dstanley4.github.io/apaTables/articles/apaTables.html}{\texttt{apaTables}}
\citep{apaTables} and
\href{http://frederikaust.com/papaja_man/}{\texttt{papaja}}
\citep{papaja} help you to create dynamically generated professional
looking results. The package
\href{https://github.com/easystats/report}{\texttt{report}}~\citep{report} is particularly noteworthy because it not only generates
tables but also a straightforward interpretation of the effects as
actual prose (e.g., it verbally quantifies the size of an effect).}

@@

\begin{quote}
\hl{Navigate to}
~\url{https://zenodo.org/login/} → Log in with GitHub
\end{quote}

@@

\begin{quote}
Log into zenodo.org → Account → \hl{GitHub}~({\url{https://zenodo.org/account/settings/github/}})
\end{quote}

@@

Again, we propose a preregistration format that closely resembles a
classic journal article but uses simulated data and dynamic document
generation to create a document that starts out as a preregistration and
eventually becomes the final report. The complete preregistration source
is available in the \hl{online supplementary material}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd}). In this section, we show code excerpts of this
preregistration (formatted in monospace) and explain the rationale
behind them.

@@

We choose the following statistical procedure because many researchers
are familiar \hl{with it}
~(The \emph{t}-test and Mann-Whitney-Wilcoxon test
  are arguably the most often used hypothesis tests (according to
 ~\citep{fagerlandTtestsNonparametricTests2012, hortonStatisticalMethodsJournal2005}
  reports that 26\% of all studies employed a \emph{t}-test and 27\% employed a
  rank-based alternative in the \emph{New England Journal of Medicine}
  in 2005). The analytical strategy presented here is, in fact,
  suboptimal in several respects (the assumption of measurement
  invariance is untested
 ~\citep{putnickMeasurementInvarianceConventions2016}, the effect size
  is underestimated in the presence of measurement error
 ~\citep{frostCorrectingRegressionDilution2000}, the effect size is
  overestimated for highly skewed distributions
 ~\citep{stonehouseRobustnessTestsCombined1998}). The interested reader
  can use the \hl{provided code for the simulation}
~\mbox{(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R})} to verify that the \emph{t}-test provides unbiased
  effect sizes but the Mann-Whitney-Wilcoxon overestimates effect sizes
  with increasing sample size and skewness.):

@@

Together with the function \texttt{simulate\_data()} (not shown here),
the function \texttt{planned\_\linebreak analysis()} can be used to justify the
planned sample size. To that end, \texttt{simulate\_data()} is
repeatedly called with increased sample sizes and the proportion of
significant results (power) is recorded. The results for such a Monte
Carlo simulation for this example are visualized in \highlighting{Figure~\ref{figure3}.}
 The code
for this power analysis can be found in the \hl{online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R}). The next snippet shows how we integrated the
results dynamically into the preregistration (the origin of the
R-variables \texttt{minn}, \texttt{choosen\_power}, and
\texttt{choosen\_d} is not shown).

@@

Following the recommendations outlined in this paper, we did not access
the data when we initially wrote this code. We therefore did not know
the exact format the data would have. This means that we did need to
change our preregistration after accessing the data to include i.e.,~the
recoding of gender (lines 17--22) and the items\hl{ (lines 23--26).}
We invite the reader to evaluate the changes we made to the preregistered code. Either on \hl{GitHub} (\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg...main})
  → ``Files changed'' or directly in Git with
  \texttt{git\ diff\ v0.0.1.1-prereg\ preregistration.Rmd}.) This is our
summary of what we changed:

@@

\begin{verbatim}
The Welch Two Sample t-test testing the difference of machiavellianism by gender
(mean in group male = 0.96, mean in group female = 0.79) suggests that the
effect is - negative, statistically significant, and small (difference = -0.17,
95% CI [0.12, 0.22], t(887.46) = 6.38, p < .001; Cohen's d = 0.43, 95% CI [0.30,
0.56])
\end{verbatim}
\end{adjustwidth}
\begin{paracol}{2}
%\linenumbers
\switchcolumn

@@

Supplementary Materials{All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454}.

@@

\funding{This research received no external funding}

\institutionalreview{Not applicable.}

\informedconsent{Not applicable.}
